### 2011-11-27 AffineLieAlgebras/Thesis/3.tex
Chapter 2 is completely translated. Description of computational package is moved to the last chapter.

\chapter{Коэффициенты ветвления и обобщенная резольвента Бернштейна-Гельфанда-Гельфанда}
\label{cha:BGG}

 \section{Обозначения}

 \label{sec:notation}
 Пусть $\frak{g}$ и $\frak{a}$ -- (аффинные) алгебры Ли, и существует вложение  $\frak{a}\hookrightarrow \frak{g}$ такое, что  $\frak{a}$ -- редуктивная подалгебра в $\frak{g}$ с согласованным корневым пространством: $\frak{%
 h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g}}^{\ast }$. Мы используем следующие обозначения:

 $\frak{g=n}^{-}+\frak{h}+\frak{n}^{+}$ --- разложение Картана;

 $r$ , $\left( r_{\frak{a}}\right) $ --- ранг алгебра $\frak{g}$ $%
 \left( \mathrm{\text{соотв., }\frak{a}}\right) $ ;

 $\Delta $ $\left( \Delta _{\frak{a}}\right) $--- корневая система; $\Delta
 ^{+} $ $\left( \mathrm{\text{соотв., }\Delta _{\frak{a}}^{+}}\right) $--- набор положительных корней (алгебр $\frak{g}$ и $\frak{a}$ соответственно);

 $\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
 \alpha \right) \right) $ --- кратность корня $\alpha$ в $%
 \Delta $ (соотв., в $\left( \Delta _{\frak{a}}\right) $);

 $S\quad \left( S_{\frak{a}}\right) $ --- множество простых корней (для 
 $\gf$ и $\af$ соответственно);

 $\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ ---  $%
 i$-й (соотв., $j$-й) простой корень алгебры $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a%
 }}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

 $\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
 }\right) $-- простой ко-корень для $\frak{g}$ $\left( \mathrm{\text{соотв.,}\frak{a}%
 }\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

 $W$ , $\left( W_{\frak{a}}\right) $--- группа Вейля;

 $C$ , $\left( C_{\frak{a}}\right) $--- фундаментальная камера Вейля;

 $\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- замыкание фундаментальной камеры Вейля;

@@

 $\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- вектор Вейля;

 $L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- интегрируемый модуль  $\frak{g}$ со старшим весом $\mu $\ ; (соотв., интегрируемый $\af$-модуль старшего веса $\nu $);

 $\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
 весовая диаграмма модуля $L^{\mu }$ (соотв., ${}L_{\frak{a}}^{\nu }$ );

 $P$ (соотв., $P_{\frak{a}} $) \ --- весовая решетка;

 $P^{+}$ (соотв., $P_{\frak{a}}^{+} $) \ --- решетка доминантных весов;

 $m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\zeta }^{\left( \nu \right)
 }\right) $ --- кратность веса $\xi \in P$ \ $\left( \mathrm{\text{соотв., }\in P_{\frak{a}}}\right) $ в $L^{\mu }$, (соотв., в $\zeta \in
 L_{\frak{a}}^{\nu } $);

 $ch\left( L^{\mu }\right) $ (соотв., $\mathrm{ch}\left( L_{\frak{a}}^{\nu
 }\right) $)--- формальный характер $L^{\mu }$ (соответственно, $L_{\frak{a}}^{\nu
 } $);

 $ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
 +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
 \mathrm{{mult}\left( \alpha \right) }}}$ --- формула Вейля-Каца;

 $R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
 mult}\left( \alpha \right) }}\quad $ (соотв., $R_{\frak{a}}:=\prod_{\alpha \in
 \Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}%
 }\left( \alpha \right) } $)--- знаменатель Вейля.

\section{Конечномерные алгебры Ли}
\label{sec:finite-dimensional}
Основные определения: корни, веса, кратности.

\section{Теория представлений аффинных алгебр Ли}
\label{sec:representation-theory}

\subsection{Алгебра петель и центральное расширение}
\label{sec:loop-algebra-central-extension}

Определение аффинных алгебр. Корни, веса, кратности. Категория О.

\subsection{Представления аффинных алгебр Ли}
\label{sec:affine-lie-algebra-representations}

\section{БГГ-резольвента}
\label{sec:bgg}
Категория О.
Резольвента Бернштейна-Гельфанда-Гельфанда для представлений аффинных алгебр Ли. Параболические модули и их связь с подалгебрами и ветвлением.

\begin{abstract}
Рекуррентные соотношения для коэффициентов ветвления основываются на определенном разложении сингулярного элемента. Мы показываем, что такое разложение может использоваться для построения параболических модулей Верма и получения обобщенных формул Вейля-Верма для характеров. Также мы демонстрируем, что коэффициенты ветвления определяют обобщенную резольвенту Бернштейна-Гельфанда-Гельфанда. 
\end{abstract}

\subsection{Введение}

\label{sec:introduction}
Свойства ветвления (аффинных) алгебр Ли важны для приложений в квантовой теории поля (смотри, например, модели конформной теории поля \cite{difrancesco1997cft},\cite{coquereaux2008conformal}). В данной работе мы показываем, что ветвление для произвольной редуктивной подалгебры связано с БГГ резольвентой и демонстрирует свойства резольвенты в категории $\mathcal{O}^{p}$ \cite{lepowsky1977generalization} (параболического обобщения категории $\mathcal{O}$ \cite{bernstein1976category}).

Резольвента для неприводимых модулей в терминах бесконечномерных модулей важна для теории интегрируемых спиновых цепочек \cite{derk1008}. В подходе  $\mathcal{Q}$-оператора Бакстера \cite{derk09} общие трансфер-матрицы, соответствующие (обобщенным) модулям Верма, факторизуются в произведение операторов Бакстера. Резольвента позволяет вычислить трансфер-матрицы для конечномерных вспомогательных пространств.

Чтобы продемонстрировать связь БГГ резольвенты с ветвлением мы используем рекурсивный подход, представленный в работе \cite
{2010arXiv1007.0318L} (аналогичный подход для максимальных вложений использовался в работе \cite{ilyin812pbc}). Мы рассматриваем подалгебру $\af \hookrightarrow \gf$ вместе с $\afb$ -- ``ортогональным партнером'' $\af$ по отношению к форме Киллинга, а также подалгебру $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$, где $\frak{h}=\frak{\frak{h}_{\af}}\oplus
\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. Для любой редуктивной подалгебры $\af$ алгебра $\afb\hookrightarrow \gf$ регулярна и редуктивна. Для интегрируемого модуля старшего веса $%
L^{\left(\mu \right) }$ и ортогональной подалгебры  $\af_{\bot }$ мы рассматриваем сингулярный элемент $\Psi ^{\left( \mu \right) }$ (числитель в формуле Вейля для характеров $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
\mu \right) }}{\Psi ^{\left( 0\right) }}$, см., например,  \cite
{humphreys1997introduction}) и знаменатель Вейля $\Psi _{\af_{\bot
  }}^{\left( 0\right) }$ для ортогонального партнера. В работе показано, что элемент  $\Psi _{\gf%
}^{\left( \mu \right) }$ может быть разложен в комбинацию числителей Вейля $\Psi _{\af_{\bot }}^{\left( \nu \right) }$, где $\nu \in P_{%
\mathfrak{a}_{\bot}}^{+}$. Это разложение дает возможность построить множество модулей старшего веса $L_{\afb}%
^{\mu _{\afb}}$. В том случае, если вложение\ $\af%
_{\bot }\hookrightarrow \gf$ \ удовлетворяет ``стандартным параболическим'' условиям, эти модули порождают параболические модули Верма $M_{\left(
\afb \hookrightarrow \gf\right) }^{\mu _{%
\afb}}$, так что исходный характер $ch\left(
L^{\mu }\right) $ в итоге раскладывается в знакопеременную сумму таких модулей. С другой стороны, если параболическое условие нарушено, конструкция сохраняется и порождает разложение по отношению к набору обобщенных модулей Верма  $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
\widetilde{\afb}}}$, где $%
\widetilde{\frak{b}_{\perp }}$ уже не является подалгеброй в $\gf$, а оказывается сжатием $\widetilde{\afb}$.

Некоторые общие свойства предложенного разложения формулируются в терминах  формального элемента $\Gamma _{\af\rightarrow \gf}$, называемого ``веером вложения''. Использование этого инструмента позволило сформулировать простой и явный алгоритм для вычисления правил ветвления, подходящий для произвольной (максимальной или не максимальной) подалгебры в аффинной алгебре Ли \cite{2010arXiv1007.0318L}.

Возможные обобщения полученных результатов обсуждаются в Разделе \ref{sec:conclusions}.

\subsection{Ортогональная подалгебра и сингулярные элементы}

\label{sec:recurr-form-branch}

В этом разделе мы покажем, как рекуррентный подход к проблеме ветвления естественным образом приводит к представлению формального характера $\frak{g}$-модуля в виде комбинации характеров, соответствующих параболическим (обобщенным) модулям Верма. Рассмотрим редуктивную алгебру Ли  $\frak{g}$ и ее редуктивную подалгебру $\frak{a}\subset \frak{g}$.
Пусть  $L^{\mu} $ -- интегрируемый модуль старшего веса алгебры  $\frak{g}$, $\mu \in P^{+}$.  Будем считать  $L^{\mu}$ вполне приводимым по отношению к подалгебре $\frak{a}$,
\begin{equation*}
L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
\end{equation*}
Это разложение может быть записано в терминах формальных характеров с использованием оператора проекции  $\pi _{\frak{a}}$ (на весовое пространство $\frak{h_{a}}^{\ast }$):
\begin{equation}
\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
\label{branching1}
\end{equation}
Для модуля  $L^{\mu }$ существует БГГ резольвента (см. \cite
{bernstein1976category,bernstein1975differential,bernstein1971structure} и
\cite{humphreys2008representations}). Все члены фильтрующей последовательности представляются суммами модулей Верма со старшими весами $\nu$, сильно связанными с $\mu$:
\begin{equation*}
\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
W\right\} .
\end{equation*}

\subsubsection{Ортогональная подалгебра}

Пусть  $\frak{h}_{\frak{a}}$ -- подалгебра Картана в  $\mathfrak{g}$. Для  $\mathfrak{a}\hookrightarrow \frak{g}$ введем ``ортогонального партнера''  $\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$.

Рассмотрим корневое подпространство  $\frak{h}_{\perp \frak{a}}^{\ast }$, ортогональное к $\frak{a}$,
\begin{equation*}
\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} ,
\end{equation*}
и корни  $\frak{g}$ (соответственно, положительные корни),  ортогональные к $\frak{a}$,
\begin{eqnarray}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
\label{delta a ort} \\
\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
\notag
\end{eqnarray}
Обозначим символом  $W_{\frak{a}_{\perp }}$ подгруппу  $W$, порожденную отражениями  $w_{\beta }$ с корнями  $\beta \in \Delta_{\frak{a}_{\perp}}^{+}$. Корневая подсистема  $\Delta _{\frak{a}_{\perp }}$ определяет подалгебру  $\frak{a}_{\perp }$, имеющую подалгебру Картана $\frak{h}_{\frak{a}_{\perp }}$. Пусть
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
h\right) =0\right\};
\end{equation*}
выделим в  $\frak{g}$  подалгебры
\begin{eqnarray}
\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp },
\qquad
\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
\end{eqnarray}
Заметим, что  $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ в общем случае не является подалгеброй в $\mathfrak{g}$.

Для подалгебр Картана имеет место разложение
\begin{equation}
\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
\frak{h}_{\frak{a}}.
\end{equation}
Рассмотрим векторы Вейля  $\rho _{\frak{a}}$ и $\rho _{\frak{a}_{\perp}} $, соответствующие  $\frak{a}$ и $\frak{a}_{\perp }$.
Введем так называемые ``дефекты'' вложения  $\mathcal{D}_{\frak{a}}$ и $\mathcal{D}_{\frak{a}_{\perp }}$:
\begin{equation}
\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho , \qquad
\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
_{\perp }}\rho .  \label{defect ort}
\end{equation}
Для  $\mu \in P^{+}$ рассмотрим связанные веса  $\left\{\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ и их проекции на $h_{\frak{a}_{\perp }}^{\ast }$, дополнительно сдвинутые на вектор дефекта $-\mathcal{D}_{\frak{a}_{\perp }}$:
\begin{equation*}
\mu _{\frak{a}_{\perp }}\left( w\right) :=\pi _{\frak{a}_{\perp }}\left[
w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad w\in W.
\end{equation*}

>>>>

\chapter{Сплинты корневых систем и функции ветвления}
\label{cha:splints}

\section{Сплинты и ветвления}
\label{sec:splints}

%%\newtheorem{Def}{Definition}[section]
%%\newtheorem{Cnj}[Def]{Conjecture}
%%\newtheorem{Prop}[Def]{Property}
%%\newtheorem{example}{Example}[section]
%%
%\input{tcilatex}

\begin{abstract}
Splint of root system for simple Lie algebra appears naturally in
studies of (regular) embeddings of reductive subalgebras. Splint can
be used to construct branching rules. We demonstrate that 
splint properties implementation drastically simplify calculations of
branching coefficients.
\end{abstract}

\section{Introduction}
\label{sec:Introduction}

Embedding $\phi$ of a root system $\Delta_1$ into a root system
$\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
subset of $\Delta$ that commutes with vector composition law in
$\Delta_{1}$ and $\Delta$.
\begin{equation*}
\phi:\Delta_1 \longrightarrow \Delta
\end{equation*}
\begin{equation*}
\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
\,\,\, \alpha,\beta \in \Delta_1
\end{equation*}

Note that the image $Im(\phi)$ must not inherit the root system
properties except the addition rules equivalent to the addition
rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
can splinter $\Delta$  when the latter can be presented 
as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.   
The term {\it splint} was
introduced by D. Richter in  \cite{richter2008splints} where the
classification of splints for simple Lie algebras was obtained.
There was also mentioned that splint must have tight
connections with the injection fan construction. The fan $\Gamma
\subset \Delta$ was
introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent
properties of branching coefficients for maximal embeddings. Injection fan is an
efficient tool to study branching rules. Later this construction
was generalized to non-maximal embeddings and infinite-dimensional
Lie algebras in \cite{2010arXiv1007.0318L, ilyin812pbc}.

In the present paper we study connections between splint and
injection fan for regular embedding of reductive subalgebras
${\mathfrak a}$ in simple Lie algebra $\mathfrak{g}$. We show that (under
certain conditions described in section \ref{sec:stems and
multiplicity functions}) splint is a natural tool to study
reduction properties of ${\mathfrak g}$-modules
with respect to a subalgebra ${\mathfrak a}\longrightarrow
{\mathfrak g}$. Using this tool we obtain the main result -- the one-to-one correspondence between weight
multiplicities in irreducible modules of splint and branching
coefficients for a reduced module $L^{\mu}_{{\mathfrak
g}\downarrow {\mathfrak a}}$.

\section{Injections and splints}

\label{sec:Injections and splints}

Consider a simple Lie algebra $\mathfrak{g}$ and its regular subalgebra $%
\mathfrak{a}\hookrightarrow \mathfrak{g}$ such that $\mathfrak{a}$
is a
reductive subalgebra $\mathfrak{a \subset g}$ with correlated root spaces: $%
\mathfrak{h}_{\mathfrak{a}}^{\ast }\subset \mathfrak{h}_{\mathfrak{g }%
}^{\ast }$. Let $\mathfrak{a}^{\mathfrak{s}}$ be a semisimple summand of
$\mathfrak{a}$,
this means that $\mathfrak{a}=\mathfrak{a}^{\mathfrak{s}} \oplus \mathfrak{u}(1)\oplus %
\mathfrak{u}(1)\oplus \dots$. We shall consider $\mathfrak{a}^{\mathfrak{s}}$
to be a proper regular subalgebra and $\mathfrak{a}$ to be the
maximal subalgebra with $\mathfrak{a}^{\mathfrak{s}}$ fixed that is the rank
$r$ of $\frak{a}$ is equal to that of $\mathfrak{g}$.

The following notations are used:

$r$ , $\left( r_{\mathfrak{a}^{\mathfrak{s}}}\right) $ --- the rank of
$\frak{g}$ $\left( \mathrm{{resp. }\mathfrak{a}^{\mathfrak{s}}}\right) $ ;

$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system;
$\Delta ^{+} $ $\left( \mathrm{{resp. }\Delta
_{\frak{a}}^{+}}\right) $--- the positive root system (of
$\frak{g}$ and $\frak{a}$ respectively);

$S \, ,\quad \left( S_{\frak{a}}\right) $ --- the system of simple roots (of $%
\frak{g}$ and $\frak{a}$ respectively);

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
i$-th (resp. $j$-th) simple root for $\frak{g}$  $\left( \mathrm{{resp. \,} \frak{%
a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
^S}\right) $;

$\omega _{i}$ , $\left( \omega _{\left( \frak{a}\right) j}\right) $ --- the $%
i$-th (resp. $j$-th) fundamental weight for $\frak{g}$ $\left( \mathrm{{resp. \,}\frak{%
a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\mathfrak{a}%
^S}\right) $;

$W$ , $\left( W_{\frak{a}}\right) $--- the corresponding Weyl group;

$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;

$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
fundamental Weyl chamber;

@@

$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;

$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\frak{a}$
-module with the highest weight $\nu $ );

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
the weight diagram of $L^{\mu }$ (resp. ${}L_{\frak{a}}^{\nu }$ );

$P$ (resp. $P_{\frak{a}} $) \ --- the weight lattice;

$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight lattice;

$\mathcal{E}$ (resp. $\mathcal{E}_{\frak{a}} $) \ --- the formal algebra;

$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
resp. }\in P_{\frak{a}}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
L_{\frak{a}}^{\nu } $);

$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\frak{a}}^{\nu
}\right) $)--- the formal character of $L^{\mu }$ (resp. $L_{\frak{a}}^{\nu
} $);

$ch\left( L^{\mu }\right)  =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }} {\prod_{\alpha \in \Delta ^{+}} \left( 1-e^{-\alpha }\right)
} $ --- the Weyl formula;

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) \quad $
(resp. $R_{\frak{a}}: =\prod_{\alpha \in \Delta_{\frak{a}}^{+}} \left(
1-e^{-\alpha }\right) $ ) --- the Weyl denominator.

Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
\[
L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
\]
\begin{equation}
\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
\label{branching1}
\end{equation}
For the modules we are interested in the Weyl formula for $\mathrm{ch}\left(
L^{\mu }\right) $ can be written in terms of singular elements \cite
{humphreys1997introduction}
\[
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
)-\rho },
\]
namely,
\begin{equation}
\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
\label{Weyl-Kac2}
\end{equation}
The same is true for submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
}\right) $ in (\ref{branching1})
\[
\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}},
\]
with
\[
\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
\]

Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
we get a relation connecting the singular elements $\Psi ^{\left( \mu
\right) }$ and $\Psi _{\frak{a}}^{\left( \nu \right) }$ :
\begin{eqnarray}
\frac{\sum_{w \in W}\epsilon (w )e^{w (\mu +\rho )-\rho }}{\prod_{\alpha \in
\Delta ^{+}}(1-e^{-\alpha })} &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu
}^{(\mu )}\frac{\sum_{w \in W_{\frak{a}}}\epsilon (w )e^{w (\nu +\rho _{%
\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
}^{+}}(1-e^{-\beta })},  \nonumber  \label{eq:4} \\
\frac{\Psi ^{\left( \mu \right) }}{R} &=&\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\frak{a}}^{\left( \nu \right) }}{R_{%
\frak{a}}}.  \label{singular main}
\end{eqnarray}

In \cite{2010arXiv1007.0318L} it was proven that branching coefficients $%
b_{\xi }^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
\hookrightarrow \frak{g}$ are subject to the set of recurrent relations:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in W/W_{\perp}}\epsilon (u)\;\dim \left( L_{\frak{a}_{\perp }}^{\mu _{\frak{a}%
_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
\widetilde{\frak{a}}}(u(\mu +\rho )-\rho )}+\right. \\
\left. +\sum_{\gamma \in \Gamma _{\widetilde{\frak{a}}\rightarrow \frak{g}%
}}s\left( \gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right)
}\right) .
\end{array}
\label{recurrent rel}
\end{equation}
where $\frak{a}_{\perp }$ is the subalgebra determined by the roots of $%
\frak{g}$ orthogonal to roots of $\frak{a}$ and $W_{\perp}$ is a Weyl group of $\mathfrak{a}_{\perp}$
\begin{eqnarray}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
\label{delta a ort}
\end{eqnarray}
\begin{eqnarray}
\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\qquad \widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }
\end{eqnarray}
and $\pi$ is the projection operator. When an injection is maximal the
projection becomes trivial and the relation (\ref{recurrent rel}) is
simplified:
\begin{equation}
\begin{array}{c}
b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in W}\epsilon (u) \delta _{\xi -\gamma _{0}, u(\mu +\rho )-\rho
}+\right. \\
\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
\gamma +\gamma _{0}\right) b_{\xi +\gamma }^{\left( \mu \right) }\right) .
\end{array}
\label{recurrent relation max}
\end{equation}
The recursion is goverened by the set $\Gamma _{\frak{a}\rightarrow \frak{g}}
$ called the injection fan. The latter is defined by the carrier set $%
\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the coefficient
function $s(\xi )$
\[
\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{ \xi \in P_{%
\frak{a}}|s(\xi )\neq 0\right\}
\]
appearing in the expansion
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\frak{a}}^{+}}\left( 1-e^{
-\alpha }\right) =-\sum_{\gamma \in P_{\frak{a}}}s(\gamma )e^{-\gamma };\quad
\label{product}
\end{equation}

Now we remind two definitions introduced in \cite{richter2008splints}

\begin{Def}
Suppose $\Delta _{0}$ and $\Delta $ are root systems with corresponding
weight lattices $P_{0}$ and $P$. Then $\phi $ is an ``embedding'',
\begin{equation}
\phi :\left\{
\begin{array}{l}
\Delta _{0}\hookrightarrow \Delta , \\
P_{0}\hookrightarrow P,
\end{array}
\right.
\end{equation}
if \newline
\noindent (a) it injects $\Delta _{0}$ in $\Delta $, and \newline
\noindent (b) acts homomorphically with respect to the vector groups in $%
P_{0}$ and $P$:
\[
\phi (\gamma )=\phi (\alpha )+\phi (\beta )
\]
for any triple $\alpha ,\beta ,\gamma \in P_{0}$ such that $\gamma =\alpha
+\beta $.
\end{Def}

$\phi$ induces an injection of formal algebras $:{\mathcal{E}}_0
\hookrightarrow \mathcal{E}$ and for the image ${\mathcal{E}}%
_i=Im_{\phi}\left( {\mathcal{E}}_0\right)$ one can consider its inverse $%
\phi^{-1}:{\mathcal{E}}_i \longrightarrow {\mathcal{E}}_0$.

Notice that one must distinguish two classes of embeddings: when the scalar
product (defined by the Killing form) in the root space $P_0$ is invariant
with respect to $\phi$ and when it is not $\phi$-invariant. The first
embedding is called "metric" , the second -- "nonmetric".

\begin{Def}
A root system $\Delta $ ''splinters'' as $(\Delta _{1},\Delta _{2})$ if
there are two embeddings $\phi _{1}:\Delta _{1}\hookrightarrow \Delta $ and $%
\phi _{2}:\Delta _{2}\hookrightarrow \Delta $ where (a) $\Delta $ is the
disjoint union of the images of $\phi _{1}$ and $\phi _{2}$ and (b) neither
the rank of $\Delta _{1}$ nor the rank of $\Delta _{2}$ exceeds the rank of $%
\Delta $.
\end{Def}

It is equivalent to say that $(\Delta_1,\Delta_2)$ is a "splint'' of $\Delta$
and we shall denote this by $\Delta \approx (\Delta_1,\Delta_2)$. Each
component $\Delta_1$ and $\Delta_2$ is a "stem'' of the splint $%
(\Delta_1,\Delta_2)$.

To study relations between injection fan technique and splint let us 
consider the case when one of the stems $\Delta _{1}=\Delta _{\frak{a}}$ 
is a root subsystem.

Splint $\Delta \approx (\Delta _{1},\Delta _{2})$ is called ''injective'' if
$\Delta _{1}=\Delta _{\frak{a}}$, is a root subsystem
in $\Delta $ corresponding to a regular reductive subalgebra $\frak{a}%
\hookrightarrow \frak{g}$.

In case of injective splint the second stem $\Delta _{\frak{s}}:=\Delta
_{2}=\Delta \setminus \Delta _{\frak{a}}$ can be translated into a product (%
\ref{product}) and it defines an injection fan $\Gamma _{\frak{a}%
\hookrightarrow \frak{g}}$. Denote by $\Delta_{\mathfrak{s}0}$ the coimage of the second embedding $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\mathfrak{g}}$.
The following conjecture follows.

\begin{Cnj}
Each injective splint $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\frak{a}%
\rightarrow \frak{g}}$ fixed by the product
\begin{equation}
\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)
=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
\end{equation}
\end{Cnj}

In case of injective splint we say that subalgebra $\frak{a}\hookrightarrow \frak{g}$
splinters $\Delta $ (and call $\frak{a}$ the ''splinting subalgebra'' of $%
\frak{g}$). In \cite{richter2008splints} splints are classified (see Appendix there)
and the first three types of them are injective.

\section{How stems define multiplicity functions}

\label{sec:stems and multiplicity functions}

In this Section we study properties of injective splints  $\Delta \approx (\Delta _{\frak{a}},\Delta _{\frak{s}})
$. It will
be demonstrated that in this case to find branching
coefficients for a splinting injection $\frak{a}\hookrightarrow
\frak{g}$ means to find weight multiplicities of an irreducible
$\frak{s}$-module $L_{\frak{s}}^{\nu }$ with fixed highest weight
$\nu $. Notice that $\frak{s}$ must not be a subalgebra of
$\frak{g}$.
